**Bayesian statistics for longitudinal studies in biomedical research**

### 2021-01-04 Manuscripts/Manuscript_AM_v1.Rmd
Updated manuscript

Mathematically speaking, if a normally distributed response $y$ is measured repeatedly at $t$ time points from  $i$ subjects in $k$ groups, the rm-ANOVA the model for the response $y_{kit}$ becomes:

@@

In this model, $\mu$ represents the group mean, $\gamma_k$ is the _fixed effect_ of each group $k$, $\tau_t$ is the fixed effect of time, and $(\gamma \tau)_{kt}$ represents the interaction of time and group effects. The term $\pi_{ik}$ represents the _random effects_ for each subject within each group. Finally, $e_{hik}$ represents the independent random error terms, which need to be normally distributed with mean 0 [@davis2002]. The model then, assumes a linear relationship between the response and the covariate.
This is better represented in the follo

_Question: How can one make a plot that tests the "limits" of the model, i.e how much "wiggliness" can this model accomodate? Make a plot to show the behavior of the model_

>>>>

Mathematically speaking, a linear model can be written as:

\begin{equation}
\label{eq:linear_model}
$$
y = \beta_0 + time * \beta_1 + treatment * \beta_2 + time * treatment * \beta_3 \\
y = \begin{cases}
\beta_0 + time * \beta_1 & \mbox{if treatment 1}\\
\beta_0 + time * \beta_1 + treatment * \beta_2 + time * treatment * \beta_3 & \mbox{if treatment 2}\\
\end{cases}
\\
$$
\end{equation}

@@

In this model, $\mu$ represents the group mean, $\gamma_k$ is the _fixed effect_ of each group $k$, $\tau_t$ is the fixed effect of time, and $(\gamma \tau)_{kt}$ represents the interaction of time and group effects. The term $\pi_{ik}$ represents the _random effects_ for each subject within each group. Finally, $e_{hik}$ represents the independent random error terms, which need to be normally distributed with mean 0 [@davis2002]. The model then, assumes a linear relationship between the response and the covariate.

The rm-ANOVA model  can be re-written under the generalized linear model  (GLM) framework [@nelder1972]. The main difference in this case is that a GLM model  uses a _linking function_ to connect the observed value to the linear model. Thus,

\begin{equation}
\label{eq:GLM}

$$
y = \beta_0 + f(time) * \boldsymbol{\beta}_1 + treatment * \beta_2 + f(time) * treatment * \boldsymbol{\beta}_3 \\
y = \begin{cases}
\beta_0 + f(time) * \boldsymbol{\beta}_1 & \mbox{if treatment 1} \\
\beta_0 + f(time) * \boldsymbol{\beta}_1 + treatment * \beta_2 + f(time) * treatment * \boldsymbol{\beta}_3 & \mbox{if treatment 2}\\
\end{cases}
\\
$$
\end{equation}

\begin{equation}
\label{eq:ANOVA_GLM}
$$y_{kit}=\mu+f(\gamma_k)+f(\tau_t)+(\gamma \tau)_{kt}+\pi_{i(k)}+e_{kit}$$
\end{equation}

The Linear model as a GLM: set $f(time) = time$ with the identity function $f(x) = x$
